Vulnerability Analysis of Container Images in Neuroimaging

### 2020-09-01 paper.tex
Updated abstract

\begin{abstract}

Today, containers, which provide operating-system level virtualization, are
popular. Correspondingly, they are widely used for scientific data analyses on 
High Performance Computing (HPC) clusters. However, the security of containers
still remains a concerning issue. Here, we focus on the security of container
images, which are often built for the entire
duration of an analysis, so scientific researchers prefer not to update
them. Consequently, their chances of containing vulnerabilities increases.  
In this study, we analyze vulnerabilities in container images used in 
HPC clusters.
We conduct two different
experiments, image update and image minimization, to report the effect 
on the number of vulnerabilities.

>>>>

\begin{abstract}
Software containers have become key technologies for the deployment of
scientific data analyses on high-performance computing (HPC)
infrastructures. They facilitate analysis portability, deployment, and
reproducibility. Container images, however, often contain slightly outdated
software packages compared to HPC environments maintained by professional
and dedicated system administrators. In addition, they often carry more
software packages than required by analyses, including compilers or unused
system librairies. As a result, container images are likely to contain
important amounts of security vulnerability, increasing the attack surface
for the entire infrastructure. This paper presents a vulnerability analysis
of container images for scientific data analysis. We analyze container
images with four vulnerability scanners, focusing on the use case of
neuroscience data analyses. We quantify the effect of images updates and
size reduction on the number of vulnerabilities, and conclude with
recommendations on how to build container images with a reduced amount of
vulnerabilities.
